---
title: "ALFRESCO outputs fact sheet"
author: "Matthew Leonawicz"
date: "April 7, 2017"
output: pdf_document
params:
  n: NA
  years: NA
  variable: NA
  x: NA
  units: NA
  regions: NA
  plot_ts: NA
  plot_den: NA
  plot_dec: NA
  rcps: NA
  gcms: NA
  veg: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
n <- params$n
yrs <- params$years
var <- params$variable
x <- params$x
uni <- params$units
reg <- params$regions
plot_ts <- params$plot_ts
plot_den <- params$plot_den
plot_dec <- params$plot_dec
rcps <- params$rcps
gcms <- params$gcms
veg <- params$veg

text_rcps <- switch(length(rcps), 
                    '1'=rcps, 
                    '2'=paste(rcps, collapse=" and "), 
                    '3'=paste0(rcps[1], ", ", paste(rcps[2:3], collapse=" and ")))
text_num_gcms <- switch(length(gcms), '1'="one", '2'="two", '3'="three", '4'="four", '5'="five")
text_models <- if(length(gcms) > 1) "models" else "model"
first_10 <- round(mean(x[1:10]))
last_10 <- round(mean(x[(n-9):n]))

dir <- "decrease"
if(last_10 > first_10) dir <- "increase" else if(last_10 == first_10) dir <- "remain stable"
proj <- if(tail(yrs, 1) > as.numeric(substr(Sys.Date(), 1, 4))) "is projected to " else ""
if(proj==""){
  if(dir=="remain stable") proj <- "remained stable" else proj <- paste0(dir, "d")
} else proj <- paste0(proj, dir)
dir2 <- if(dir=="decrease") "reduction" else "gain"
```

## Testing...

Simulations of `r tolower(var)` are shown for the period `r yrs[1]` through `r yrs[n]`.
In this time the `r tolower(var)` per year `r proj` from an average of $`r first_10`$ `r uni` during the first ten years
to an average of $`r last_10`$ `r uni` per year during the final ten years of the period.
This change of $`r abs(last_10 - first_10)`$ `r uni` in the `r reg` represents 
a `r round(100*abs(1-last_10/first_10))` percent `r dir2` in `r tolower(var)`.

This applies to `r tolower(veg)`.
These results are based on emissions scenarios `r text_rcps` and `r text_num_gcms` climate `r text_models`.

## Plots

Embedding plots...

```{r plot_ts}
plot_ts
```

```{r plot_den}
plot_den
```

```{r plot_dec}
plot_dec
```
