---
title: Baseline Fire 1950 - 2009 \\ \large Unvetted preliminary rush draft from developmental code
author: Matthew Leonawicz
output:
  html_document:
    toc: false
    theme: united
    highlight: tango
    keep_md: true
---

```{r knitr_setup, include=FALSE, cache=FALSE}
library(knitr)
opts_chunk$set(results='asis', cache=FALSE, echo=FALSE, eval=TRUE, tidy=TRUE, message=FALSE, warning=FALSE, dpi=300, fig.height=7, fig.width=10.5)
read_chunk("../../code/baseline_fire.R")
```

```{r setup, cache=TRUE}
```

## Baseline Fire Tables
The third table down combining the first two relates to table 3.1 in the original document.
This uses strictly ALFRESCO output.

```{r baseline_fire_setup, cache=TRUE, results="hide"}
```

### Fire frequency (fires/year)
```{r baseline_fire_fc_table}
```

### Burn area (km^2/year)
```{r baseline_fire_ba_table}
```

## Baseline Fire Graphs
The below graph relates to figure 3.2 in the original document.
This uses strictly ALFRESCO output.

### Alaska
```{r baseline_fire_barplot_AK, fig.width=7, fig.height=4, fig.cap="Alaska", fig.pos="H"}
```

### LCC Regions
All five following separate LCC graphs relate to figure 3.3 in the original document.
This uses strictly ALFRESCO output.

#### Arctic
```{r baseline_fire_barplot_LCC1, fig.width=7, fig.height=4, fig.cap="Arctic", fig.pos="H"}
```

#### North Pacific
```{r baseline_fire_barplot_LCC2, fig.width=7, fig.height=4, fig.cap="North Pacific", fig.pos="H"}
```

#### Northwest Interior Forest North
```{r baseline_fire_barplot_LCC3, fig.width=7, fig.height=4, fig.cap="Northwest Interior Forest North", fig.pos="H"}
```

#### Northwest Interior Forest South
```{r baseline_fire_barplot_LCC4, fig.width=7, fig.height=4, fig.cap="Northwest Interior Forest South", fig.pos="H"}
```

#### Western Alaska
```{r baseline_fire_barplot_LCC5, fig.width=7, fig.height=4, fig.cap="Western Alaska", fig.pos="H"}
```

