---
title: "R code: Baseline Fire 1950 - 2009"
author: Matthew Leonawicz
output:
  html_document:
    toc: false
    theme: united
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, include=FALSE, cache=FALSE}
library(knitr)
opts_chunk$set(results='asis', cache=FALSE, echo=TRUE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/baseline_fire.R")
```

Note that the code may contain seemingly unnecessary repetition across multiple code chunks.
Sometimes I do this when using `knitr` to knit documents.
If I was strictly outputing graphics files I would remove apparent duplicate code.

Also note in the `modnames <-` assignment that the same script is simply run twice, once for each climate model.
The amount of hardcoding present in general is indicative of the limited time available for the task.

Depending on whether the output documents are md/html or LaTeX/pdf, tables are compiled differently as well using `xtable`.

```{r setup, cache=TRUE}
```

## Baseline Fire Tables
```{r baseline_fire_setup, cache=TRUE}
```

### Fire frequency (fires/year)
```{r baseline_fire_fc_table}
```

### Burn area (km^2/year)
```{r baseline_fire_ba_table}
```

## Baseline Fire Graphs
### Alaska
```{r baseline_fire_barplot_AK, fig.width=7, fig.height=4, fig.cap="Alaska", fig.pos="H"}
```

### LCC Regions
#### Arctic
```{r baseline_fire_barplot_LCC1, fig.width=7, fig.height=4, fig.cap="Arctic", fig.pos="H"}
```

#### North Pacific
```{r baseline_fire_barplot_LCC2, fig.width=7, fig.height=4, fig.cap="North Pacific", fig.pos="H"}
```

#### Northwest Interior Forest North
```{r baseline_fire_barplot_LCC3, fig.width=7, fig.height=4, fig.cap="Northwest Interior Forest North", fig.pos="H"}
```

#### Northwest Interior Forest South
```{r baseline_fire_barplot_LCC4, fig.width=7, fig.height=4, fig.cap="Northwest Interior Forest South", fig.pos="H"}
```

#### Western Alaska
```{r baseline_fire_barplot_LCC5, fig.width=7, fig.height=4, fig.cap="Western Alaska", fig.pos="H"}
```

