---
title: Projected fire change 2000 - 2099 \\ \large Unvetted preliminary rush draft from developmental code
author: Matthew Leonawicz
output:
  html_document:
    toc: false
    theme: united
    highlight: tango
    keep_md: true
---

```{r knitr_setup, include=FALSE, cache=FALSE}
library(knitr)
opts_chunk$set(results='asis', cache=FALSE, echo=FALSE, eval=TRUE, tidy=TRUE, message=FALSE, warning=FALSE, dpi=300, fig.height=7, fig.width=10.5)
read_chunk("../../code/fire_change.R")
```

```{r setup, cache=TRUE}
```

## Projected fire change tables
In each subsection below, the third table down with percentages relates to table 8.1 in the original document.
This uses strictly ALFRESCO output.
The tables use years 2000 - 2009 and 2090 - 2099.
There is one section for each region, Alaska and the five LCCs.

```{r fire_change_setup, cache=TRUE, results="hide"}
```

### Alaska
#### Historical fire
```{r fire_change_table1_AK}
```

#### Projected fire
```{r fire_change_table2_AK}
```

#### Percent change
```{r fire_change_table_dif_AK}
```

### Arctic
#### Historical fire
```{r fire_change_table1_LCC1}
```

#### Projected fire
```{r fire_change_table2_LCC1}
```

#### Percent change
```{r fire_change_table_dif_LCC1}
```

### North Pacific
#### Historical fire
```{r fire_change_table1_LCC2}
```

#### Projected fire
```{r fire_change_table2_LCC2}
```

#### Percent change
```{r fire_change_table_dif_LCC2}
```

### Northwest Interior Forest North
#### Historical fire
```{r fire_change_table1_LCC3}
```

#### Projected fire
```{r fire_change_table2_LCC3}
```

#### Percent change
```{r fire_change_table_dif_LCC3}
```

### Northwest Interior Forest South
#### Historical fire
```{r fire_change_table1_LCC4}
```

#### Projected fire
```{r fire_change_table2_LCC4}
```

#### Percent change
```{r fire_change_table_dif_LCC4}
```

### Western Alaska
#### Historical fire
```{r fire_change_table1_LCC5}
```

#### Projected fire
```{r fire_change_table2_LCC5}
```

#### Percent change
```{r fire_change_table_dif_LCC5}
```

## Percentile fire trends by scenario
The below graph relates to figure 8.2 in the original document.
This uses strictly ALFRESCO output.

### Alaska
```{r fire_change_ts_AK, fig.width=7, fig.height=3, fig.cap="Alaska", fig.pos="H"}
```

All five following separate LCC graphs relate to figure 8.3 in the original document.
This uses strictly ALFRESCO output.

### Arctic
```{r fire_change_ts_LCC1, fig.width=7, fig.height=3, fig.cap="Arctic", fig.pos="H"}
```

### North Pacific
```{r fire_change_ts_LCC2, fig.width=7, fig.height=3, fig.cap="North Pacific", fig.pos="H"}
```

### Northwest Interior Forest North
```{r fire_change_ts_LCC3, fig.width=7, fig.height=3, fig.cap="Northwest Interior Forest North", fig.pos="H"}
```

### Northwest Interior Forest South
```{r fire_change_ts_LCC4, fig.width=7, fig.height=3, fig.cap="Northwest Interior Forest South", fig.pos="H"}
```

### Western Alaska
```{r fire_change_ts_LCC5, fig.width=7, fig.height=3, fig.cap="Western Alaska", fig.pos="H"}
```

