---
title: "R code: Projected Vegetation Change 2009 vs. 2100"
author: Matthew Leonawicz
output:
  html_document:
    toc: false
    theme: united
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, include=FALSE, cache=FALSE}
library(knitr)
opts_chunk$set(results='asis', cache=FALSE, echo=TRUE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/vegetation_change.R")
```

Note that the code may contain seemingly unnecessary repetition across multiple code chunks.
Sometimes I do this when using `knitr` to knit documents.
If I was strictly outputing graphics files I would remove apparent duplicate code.

Also note in the `modnames <-` assignment that the same script is simply run twice, once for each climate model.
The amount of hardcoding present in general is indicative of the limited time available for the task.

Depending on whether the output documents are md/html or LaTeX/pdf, tables are compiled differently as well using `xtable`.

```{r setup, cache=TRUE}
```

```{r veg_change_setup, cache=TRUE}
```

## Percent Change by Vegetation Class
### 2009 Baseline by Scenario
#### Alaska
```{r baseline_veg_barplot_AK1, fig.width=7, fig.height=6, fig.cap="Alaska", fig.pos="H"}
```
```{r baseline_veg_barplot_AK2, fig.width=7, fig.height=4, fig.cap="Alaska", fig.pos="H"}
```

#### Arctic
```{r baseline_veg_barplot_LCC1a, fig.width=7, fig.height=6, fig.cap="Arctic", fig.pos="H"}
```
```{r baseline_veg_barplot_LCC1b, fig.width=7, fig.height=4, fig.cap="Arctic", fig.pos="H"}
```

#### North Pacific
```{r baseline_veg_barplot_LCC2a, fig.width=7, fig.height=6, fig.cap="North Pacific", fig.pos="H"}
```
```{r baseline_veg_barplot_LCC2b, fig.width=7, fig.height=4, fig.cap="North Pacific", fig.pos="H"}
```

#### Northwest Interior Forest North
```{r baseline_veg_barplot_LCC3a, fig.width=7, fig.height=6, fig.cap="Northwest Interior Forest North", fig.pos="H"}
```
```{r baseline_veg_barplot_LCC3b, fig.width=7, fig.height=4, fig.cap="Northwest Interior Forest North", fig.pos="H"}
```

#### Northwest Interior Forest South
```{r baseline_veg_barplot_LCC4a, fig.width=7, fig.height=6, fig.cap="Northwest Interior Forest South", fig.pos="H"}
```
```{r baseline_veg_barplot_LCC4b, fig.width=7, fig.height=4, fig.cap="Northwest Interior Forest South", fig.pos="H"}
```

#### Western Alaska
```{r baseline_veg_barplot_LCC5a, fig.width=7, fig.height=6, fig.cap="Western Alaska", fig.pos="H"}
```
```{r baseline_veg_barplot_LCC5b, fig.width=7, fig.height=4, fig.cap="Western Alaska", fig.pos="H"}
```

### 2100 Percent Change by Scenario
#### Alaska
```{r veg_change_barplot_AK1, fig.width=7, fig.height=6, fig.cap="Alaska", fig.pos="H"}
```
```{r veg_change_barplot_AK2, fig.width=7, fig.height=4, fig.cap="Alaska", fig.pos="H"}
```

#### Arctic
```{r veg_change_barplot_LCC1a, fig.width=7, fig.height=6, fig.cap="Arctic", fig.pos="H"}
```
```{r veg_change_barplot_LCC1b, fig.width=7, fig.height=4, fig.cap="Arctic", fig.pos="H"}
```

#### North Pacific
```{r veg_change_barplot_LCC2a, fig.width=7, fig.height=6, fig.cap="North Pacific", fig.pos="H"}
```
```{r veg_change_barplot_LCC2b, fig.width=7, fig.height=4, fig.cap="North Pacific", fig.pos="H"}
```

#### Northwest Interior Forest North
```{r veg_change_barplot_LCC3a, fig.width=7, fig.height=6, fig.cap="Northwest Interior Forest North", fig.pos="H"}
```
```{r veg_change_barplot_LCC3b, fig.width=7, fig.height=4, fig.cap="Northwest Interior Forest North", fig.pos="H"}
```

#### Northwest Interior Forest South
```{r veg_change_barplot_LCC4a, fig.width=7, fig.height=6, fig.cap="Northwest Interior Forest South", fig.pos="H"}
```
```{r veg_change_barplot_LCC4b, fig.width=7, fig.height=4, fig.cap="Northwest Interior Forest South", fig.pos="H"}
```

#### Western Alaska
```{r veg_change_barplot_LCC5a, fig.width=7, fig.height=6, fig.cap="Western Alaska", fig.pos="H"}
```
```{r veg_change_barplot_LCC5b, fig.width=7, fig.height=4, fig.cap="Western Alaska", fig.pos="H"}
```

