---
title: Projected Vegetation Trends 2009 - 2100 \\ \large Unvetted preliminary rush draft from developmental code
author: Matthew Leonawicz
output:
  html_document:
    toc: false
    theme: united
    highlight: tango
    keep_md: true
---

```{r knitr_setup, include=FALSE, cache=FALSE}
library(knitr)
opts_chunk$set(results='asis', cache=FALSE, echo=FALSE, eval=TRUE, tidy=TRUE, message=FALSE, warning=FALSE, dpi=300, fig.height=3.5, fig.width=7)
read_chunk("../../code/vegetation_change.R")
```

```{r setup, cache=T}
```

```{r veg_change_setup, cache=TRUE, results="hide"}
```

## Area Trends by Vegetation Class and Scenario
The below graph relates to figure 6.3 in the original document.
This uses strictly ALFRESCO output.

### Alaska
```{r veg_change_ts_AK, fig.cap="Alaska", fig.pos="H"}
```

All five following separate LCC graphs relate to figure 6.3 in the original document.
This uses strictly ALFRESCO output.

### Arctic
```{r veg_change_ts_LCC1, fig.cap="Arctic", fig.pos="H"}
```

### North Pacific
```{r veg_change_ts_LCC2, fig.cap="North Pacific", fig.pos="H"}
```

### Northwest Interior Forest North
```{r veg_change_ts_LCC3, fig.cap="Northwest Interior Forest North", fig.pos="H"}
```

### Northwest Interior Forest South
```{r veg_change_ts_LCC4, fig.cap="Northwest Interior Forest South", fig.pos="H"}
```

### Western Alaska
```{r veg_change_ts_LCC5, fig.cap="Western Alaska", fig.pos="H"}
```

