---
output:
  html_document:
    toc: false
    theme: cosmo
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=TRUE, echo=FALSE, tidy=TRUE, message=FALSE, warning=FALSE, dpi=300, fig.height=7.5, fig.width=10.5)
library(printr)
read_chunk("../../code/gs_eda.R")
```

##
##
## Introduction

The following sections provide exploratory plots and tables relating to thaw degree days (TDD) for the Growing Season project.

```{r setup2}
```

```{r plot_setup}
```

First, here is a map of the ecoregions currently in use for the project.

```{r plot_eco, fig.height=7, fig.width=12}
```

### Marginal distributions

#### TDD by threshold and ecoregion

This plot shows probability density fucntions (pdfs) for TDD colored by percent TDD threshold and paneled by ecoregion.
These marginal densities integrate over space (map pixels) and time (years, 1982 - 2010).

```{r plot_marginal_tdd_01a}
```

Subsequent sections look more closely at TDD in space and time, separately and in combination.
