---
title: "Introduction to snapmeta"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to snapmeta}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.path = "man/figures/README-", eval = TRUE,
  message = FALSE, warning = FALSE, error = FALSE, tidy = TRUE
)
```

`snapmeta` contains a collection of utility functions for the development of other SNAPverse packages.
`snapmeta` is a satellite package of the SNAPverse collection of R packages.

## Package setup

The biggest convenience of `snapmeta` is the streamlined, semi-automated SNAPverse package creation setup process.
First, take a look at the helpful reminders in the console output from `reminders`.
It will be somewhat specific to your account and project if you pass arguments.
For example, using my defaults:

```{r load, echo=FALSE}
library(snapmeta)
```

```{r reminders, eval=FALSE}
library(snapmeta)
reminders()
```

This should all be familiar if you develop R packages, but it can be easy to occasionally neglect a step.
The recommendations are not completely universal, however, and cater specifically to SNAPverse package development.

If it meets all needs, run:

```{r use_these, eval=FALSE}
use_these()
```

If something different is needed, ignore the above wrapper function.
Instead, make individual calls to whichever package setup functions are required.

## Getting info from the verse

A table of all SNAPverse packages can be obtained by:

```{r sv_pkgs}
sv_pkgs()
```

The table includes columns giving the section of the verse a package belongs to and whether or not a local git repository/R source package
exists sharing the same parent directory as the current package (current working directory).
A short list of the latter existing local packages can be obtained by:

```{r sv_local_pkgs}
sv_local_pkgs()
```

## Shiny apps support

`snapmeta` is also used to assist the `snapapps` package with integrating new Shiny apps into its collection. `snapapps` is an R package in the apps and docs sector of the SNAPverse that essentially serves as a repository of SNAP Shiny app examples in package form.

While in the process of developing or updating `snapapps` an new Shiny app can be conveniently added to the package.
As the name suggests, id may be vectorized so that you can add multiple apps at once.

```{r use_apps, eval=FALSE}
use_apps(id = c("my_new_app1", "my_new_app2"))
```

By default this will also add a template `DESCRIPTION` file and template `Readme.md` file to the package now inside `snapapps`.
It is assumed the app does not already have these. If it does, set `description` and `readme` to `FALSE`.
These files can also be added later on using `use_appdesc` and `use_appreadme`.
This also gives more control over the content output by `use_appdesc`.

```{r use_templates, eval=FALSE}
use_appdesc("path/to/my_new_app1", title = "My first app", author = "Me", url = "example.com", tags = c("data analysis", "graphing"))
use_appreadme()
```

These functions are intended for using during `snapapps` development and maintenence but can just as easily be used for including Shiny app examples in any R package.
