---
title: "Introduction to snaplocs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to snaplocs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.path = "man/figures/README-",
  message = FALSE, warning = FALSE, error = FALSE, tidy = TRUE
)
```

`snaplocs` is as package in the functional sector of the SNAPverse. Like most packages, it contains some form of data. However, it is not a data sector package. Data packages are those that contain a large enough amount of data to warrant a standalone package so that functional packages remain small.
This is not one of those packages. Unlike `snappoly` and `snapgrid` it does not contain any maps. `snaplocs` contains point location data in a single data frame. There are 3,914 locations in all, spread across Alaska and western Canada. Compared to SNAPverse data packages, this is quite small.

While `snaplocs` is nevertheless still typically treated as a data package for basic access to the `locs` data set, the package does provide a collection of functions for working with the data. This vignette provides example usage of several functions.

## Point location data

Print a summary of the data.

```{r tibble, echo=FALSE}
library(tibble)
```

```{r print}
library(snaplocs)
locs
```

## Metadata helpers

There are some basic helper functions that grab metadata associated with point locations of interest.

```{r helpers}
x <- "Fairbanks"
get_state(x)
get_country(x)
get_coords(x)
```

These calls also take vectors and `get_coords` with `keep_cols = TRUE` retains all columns of `locs`.

```{r helpers2}
x <- c("Fairbanks", "Calgary")
get_state(x)
get_country(x)
get_coords(x)
get_coords(x, keep_cols = TRUE)
```

Typically a user is interested in all communities, or all those in a particular province.
Less commonly, a user may have a specific location name and query the table as demonstrated above.
Not only must the name be exact, but the results returned may not be unique.
These helper functions that take specific locations as input are only intended to provide rough convenience.
For example, Galena is not unique.

```{r helpers3}
x <- c("Galena")
get_state(x)
get_country(x)
get_coords(x)
get_coords(x, keep_cols = TRUE)
```

An additional `group` argument can be passed to any of these functions to protect against this possibility.
`group` may be a vector.

```{r helpers4}
grp <- "Alaska"
get_state(x, group = grp)
get_country(x, grp)
get_coords(x, grp)
get_coords(x, grp, keep_cols = TRUE)
```

## Spatial reprojection

Alaska- and western Canada-centric projects at SNAP often use data in a NAD83 Alaska Albers equal area conic projection.
To quickly convert a 2-column matrix or data frame of WGS84 lon/lat coordinates to a 2-column matrix in this projection, do the following:

```{r albers}
wgs2ak(get_coords(x))
head(wgs2ak(locs[3:4]))
```

More functions will be added in the next package revision.
