---
output:
  html_document:
    toc: false
    theme: flatly
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/alfresco/alf_gcmRuns_inputPrep.R")
```

##
##
## alf_gcmRuns_inputPrep.R

The `alf_gcmRuns_inputPrep.R` script prepares geotiff outputs from Noatak domain, CRU 3.2-based, historical calibration ALFRESCO runs for use as inputs to future GCM-based runs.
Historical runs end with year 2013.
2013 geotiffs for age, vegetation, and burn severity history are copied from the final calibrated outputs directory to a new location to be referenced by future ALFRESCO run JSON input files.

In the process, the extents of these geotiffs are enlarged with NA-padding to match that of a template raster layer.
The template is an input geotiff to the original historical calibration runs.
This is necessary because the Noatak runs are set to trim inputs and run on a smaller domain as well as maintain trimming in the resultant output files.
ALFRESCO will throw an exception is trimmed output geotiffs with a smaller spatial extent are then passed as inputs to a new run along with other fixed inputs of larger extent.

## R code

### Input file preparation

```{r prep_files}
```
