---
output:
  html_document:
    toc: false
    theme: flatly
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/alfresco/AlfrescoFRP.R")
```

##
##
## AlfrescoFRP.R

The `AlfrescoFRP.R` script carries out post-processing of ALFRESCO simulation outputs.
It is assumed that `AlfrescoCalibration.R` has already executed. This and any other post-processing **R** script are always run secondary to the primary script.
The key features of the script include:

*    Simulation replicate-specific spatially explicit maps of Fire Return Period (FRP) compared with a historically observed FRP map.
*    .RData workspace files containing Fire Return Interval (FRI) and FRP data frames for use in other applications.
*    Export of **R** data objects via **R** workspace to a template Shiny app for dynamic, interactive exploratory analysis by the user.

Files of interest are attached to an email which is sent from the Atlas cluster to intended recipients as part of the broader SLURM process.
This script is called by the SLURM script, `CompileData.slurm` after the initial post-processing script, `AlfrescoCalibration.R` has run.
This script also sources `obs_fire_setup.R` during runtime.

## R code

### Setup

```{r setup}
```

### Processing function: modeled outputs

```{r func_modeled}
```

### Processing function: observed data

```{r func_empirical}
```

### Observational data-specific setup

```{r empirical_data_setup}
```

### Processing

```{r run}
```

### Spatially explicit FRP maps

```{r FRP_maps}
```

### Shiny app setup

```{r FRP_app_setup}
```

### Save outputs

```{r save}
```
