---
output:
  html_document:
    toc: false
    theme: flatly
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, echo=TRUE, tidy=TRUE, message=FALSE, warning=FALSE, dpi=300, fig.height=10.5, fig.width=10.5)
read_chunk("../../code/flammability_maps/flam_trunc.R")
```

##
##
## Truncation of flammability distributions

Flammability distributions in each map layer are trimmed at a lower and upper bound.
Truncations are unique to each vegetation class' flammability distribution.
Bounds are the critical values pertaining to the 10th and 90th percentiles of the global flammability distribution.
The global distribution refers to the distribution of flammability values through time (1950 - 2013) and across space for an individual vegetation class.

Lower and upper bounds for each vegetation class can be seen in the code below and are based on explorations of the distributions carried out in the `flam_dist.R` script.
The distribution of the aggregate CAVM tundra class, which combines shrub, graminoid, and wetland tundra, is also trimmed with respect to its global 10th and 90th percentiles.

### R code

```{r setup}
```

```{r func}
```

```{r run}
```
