---
output:
  html_document:
    toc: false
    theme: flatly
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/tpByVeg/tpByVeg_CMIP5.R")
```

##
##
## tpByVeg_CMIP5.R

The `tpByVeg_CMIP5.R` script calculates mean temperature and precipitation over all grid cells in CRU 3.2 map layers conditional on vegetation class using a given vegetation classification map.
Alternatively, instead of computing an overall mean, the script can be passed arguments to specify sampling of climate values and a sample size.
These vegetation-specific climate means and/or samples are used as variables in gradient boosting machine (GBM), or generalized boosted regression modeling.
The resulting GBM models are used to develop climate-driven, vegetation-mediated flammability maps with a distinct nonlinear fire responses to climate for each vegetation class.
These flammability maps are used in ALFRESCO in lieu of the original temperature and precipitation maps.

## R code

### Setup

```{r setup}
```

### Processing function

```{r func}
```

### Run

```{r run}
```

### Save outputs

```{r save}
```
