---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.path = "man/figures/README-",
  message = FALSE, warning = FALSE, error = FALSE, tidy = TRUE
)
```
# snaplocs

[![Travis-CI Build Status](https://travis-ci.org/leonawicz/snaplocs.svg?branch=master)](https://travis-ci.org/leonawicz/snaplocs)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/leonawicz/snaplocs?branch=master&svg=true)](https://ci.appveyor.com/project/leonawicz/snaplocs)
[![Coverage Status](https://img.shields.io/codecov/c/github/leonawicz/snaplocs/master.svg)](https://codecov.io/github/leonawicz/snaplocs?branch=master)

The `snaplocs` package provides functions for working with point location data used in various applications and projects by the Scenarios Network for Alaska and Arctic Planning at the University of Alaska Fairbanks. Point location data is included. Locations include major and minor cities, towns, villages, and some other locations such as mines. This package is part of the [SNAPverse](https://leonawicz.github.io/snapverse/) collection of R packages.

## Installation

You can install snaplocs from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("leonawicz/snaplocs")
```

```{r is_md, echo = FALSE}
is_md <- knitr::opts_knit$get("rmarkdown.pandoc.to") == "markdown_github-ascii_identifiers"
```

```{r md_pkg_ref, echo = FALSE, results = "asis", eval = is_md}
cat('## Reference\n\n[Complete package reference and function documentation](https://leonawicz.github.io/snaplocs/)')
```
